Place of death in NRS COVID-19 deaths

### 2021-03-31 covid_nrs_place_of_death.Rmd
incorporated "main report" from nrs website so I can do breakdown of weekly deaths by cause of death... hope it works next week!
also started making some visualisations of cause of death

```{r}
latest_data_date <- strftime(max(table_of_data_sources$last_modified), format="%F")

dir_outputs <- paste0("./outputs/",latest_data_date)
if (!dir.exists(dir_outputs)) dir.create(dir_outputs)
```

@@

@@

files_weekly_deaths <- set_names(x = as.list(table_of_data_sources$path_latest), nm = table_of_data_sources$short_name)

# checking out structure

@@

beds_raw <- 
  read_csv("C:/Users/janwork/Downloads/beds_by_nhs_board_of_treatment_and_specialty.csv", guess_max = 3e4) %>%
  mutate(ref_area = match_area(HB)) %>%  # clean health board names
  clean_names() %>%
  # select(-percentage_occupancy_qf) %>%
  extract(col = quarter, into = c("year", "quarter"), regex = "(\\d{4})Q(\\d)", remove = TRUE) %>%
  # mutate(across(.cols = matches("percent"), .fns = ~{.x / 100}))
  mutate(percentage_occupancy = percentage_occupancy / 100)

beds_raw %>%
  filter(ref_area == "Scotland") %>% count(specialty_name)

beds_raw %>%
  filter(ref_area == "Scotland" & specialty_name == "Palliative Medicine") %>%
  ggplot() +
  aes(x = quarter, y = percentage_occupancy, colour = year, size = year) +
  scale_y_continuous(labels = function(x) scales::percent(x), limits = c(0,NA)) +
  # geom_point() +
  geom_line(aes(group = year)) +
  scale_colour_viridis_d() +
  scale_size_manual(values = c(rep(0.5, times = 5),1)) +
  NULL

@@

historical_weekly_averageoverall <-
  past_deaths_overall %>%
  filter(year!="average") %>%  # remove averages
  group_by(year, week_number) %>%  # remove week 53 if it was 0 for all places  - this means there was no week 53!
  filter(!all(number_of_deaths==0 & week_number==53)) %>%
  ungroup %>%
  create_week_53_data_for_years_with_52_weeks %>%
  ungroup %>%
  group_by(week_number,place_of_death) %>% 
  summarise(
    across(number_of_deaths, .fns = list(mean=mean,min=min,max=max)),
    .groups = "drop"
  ) %>% rename_all(~str_replace_all(.x, pattern = "number_of_deaths", replacement = "deaths"))

@@

historical_weekly_averagehb <-
  past_deaths_hb %>%
  create_week_53_data_for_years_with_52_weeks() %>%
  group_by(
    week_number, place_of_death, ref_area
  ) %>%
  summarise(
    deaths_mean = mean(number_of_deaths),
    deaths_min = min(number_of_deaths),
    deaths_max = max(number_of_deaths),
    .groups = "drop"
  )

historical_weekly_averagela <-
  past_deaths_la %>%
  create_week_53_data_for_years_with_52_weeks() %>%
  group_by(
    week_number, place_of_death, ref_area
  ) %>%
  summarise(
    deaths_mean = mean(number_of_deaths),
    deaths_min = min(number_of_deaths),
    deaths_max = max(number_of_deaths),
    .groups = "drop"
  )

historical_weekly_averagesex_age <-
  past_deaths_sex_age %>%
  create_week_53_data_for_years_with_52_weeks() %>%
  group_by(
    week_number, place_of_death, age, sex
  ) %>%
  summarise(
    deaths_mean = mean(number_of_deaths),
    deaths_min = min(number_of_deaths),
    deaths_max = max(number_of_deaths),
    .groups = "drop"
  )

historical_weekly_averageage <-
  past_deaths_age %>%
  create_week_53_data_for_years_with_52_weeks() %>%
  group_by(
    week_number, place_of_death, age
  ) %>%
  summarise(
    deaths_mean = mean(number_of_deaths),
    deaths_min = min(number_of_deaths),
    deaths_max = max(number_of_deaths),
    .groups = "drop"
  )

historical_weekly_averagesex <-
  past_deaths_sex %>%
  create_week_53_data_for_years_with_52_weeks() %>%
  group_by(
    week_number, place_of_death, sex
  ) %>%
  summarise(
    deaths_mean = mean(number_of_deaths),
    deaths_min = min(number_of_deaths),
    deaths_max = max(number_of_deaths),
    .groups = "drop"
  )

@@

historical_annual_average_age <-
  past_deaths_age %>%
  compute_historical_annual_average_deaths(age)
```

@@

```{r}
weekly_deaths_overall %>%
  filter(sex=="all" & age=="all") %>%
  left_join(historical_weekly_averageoverall) %>%
  select(year, week_number, place_of_death, deaths_nrs_past_average_all_causes, deaths_mean) %>%
  filter(round(deaths_nrs_past_average_all_causes) != round(deaths_mean)) %>%
  knitr::kable(caption = "Subset of weekly deaths where calculated mean deaths 2015-2019 differed between the COVID-19 related deaths file and the weekly deaths file (i.e. all other entries had the same figures!). Week 53 was computed as the average of deaths in week 53 in 2015 and week 52 in 2016-2019. For all the other datasets the mean deaths computed agree!")
```

@@

historical_weekly_averagehb <- compute_moving_average_for_historical_data(historical_weekly_averagehb)
historical_weekly_averagela <- compute_moving_average_for_historical_data(historical_weekly_averagela)
historical_weekly_averagesex_age <- compute_moving_average_for_historical_data(historical_weekly_averagesex_age)
historical_weekly_averagesex <- compute_moving_average_for_historical_data(historical_weekly_averagesex)
historical_weekly_averageage <- compute_moving_average_for_historical_data(historical_weekly_averageage)
```

@@

```{r}
## compute rolling average
merged_deaths_overall <-
  weekly_deaths_overall %>%
  filter(sex=="all" & age=="all") %>%
  inner_join(historical_weekly_averageoverall %>% mutate(sex = "all", age = "all"),  # only merge for aggregated data b/c that's all we have!
            by = c("place_of_death", "week_number", "sex", "age"))

merged_deaths_hb <-
  rolling_deaths_hb %>%  # use data with rolling movingincluded
  inner_join(historical_weekly_averagehb, by = c("week_number","ref_area","place_of_death"))

merged_deaths_la <-
  rolling_deaths_la %>%  # use data with rolling movingincluded
  inner_join(historical_weekly_averagela, by = c("week_number","ref_area","place_of_death"))

merged_deaths_sex_age <-
  rolling_deaths_sex_age %>%  # use data with rolling movingincluded
  inner_join(historical_weekly_averagesex_age, by = c("place_of_death", "week_number", "sex", "age"))

merged_deaths_sex <-
  rolling_deaths_sex %>%
  inner_join(historical_weekly_averagesex, by = c("place_of_death", "week_number", "sex"))

merged_deaths_age <-
  rolling_deaths_age %>%
  inner_join(historical_weekly_averageage, by = c("place_of_death", "week_number", "age"))
```

@@

total_deaths_overall <-
  merged_deaths_overall %>%
  compute_total_deaths_in_year() %>%
  left_join(historical_annual_average_overall, by = c("place_of_death")) %>%
  compute_ratio_of_annual_deaths_to_historical
```

@@

date_range_text <- glue::glue("Data from w/c {format(min(weekly_deaths_overall$date_w_c), '%d %B %Y')} to w/c {format(max(weekly_deaths_overall$date_w_c), '%d %B %Y')} (inclusive).")

@@

## Overall deaths at home 2020 by cause of death

```{r}
# TODO: add yearly range for all deaths
# TODO: split data by covid-underlying cause of desath & covid-factor in death
merged_deaths_overall %>%
  filter(sex=="all", age=="all") %>%
  filter(year==2020) %>%
  filter(place_of_death == "Home & other non-institution") %>%
  group_by(ref_area, year) %>%
  summarise(
    deaths_all_causes = sum(deaths_all_causes, na.rm=TRUE),
    deaths_covid_related = sum(deaths_covid_related, na.rm=TRUE),
    deaths_non_covid = sum(deaths_non_covid, na.rm=TRUE)
  )
```

>>>>

```{r}
latest_data_modified_date <- strftime(max(table_of_data_sources$last_modified), format="%F")

dir_outputs <- paste0("./outputs/",latest_data_modified_date)
if (!dir.exists(dir_outputs)) dir.create(dir_outputs)
```

@@

### Define locations for weekly data fiels

@@

files_weekly_deaths <- set_names(x = as.list(table_of_data_sources$path_latest), nm = table_of_data_sources$short_name)
```

### Load  'main report' data

We are only loading deaths aggregated by cause from the 'main report' data! These are compiled in two sheets:

* Table 3 (2020)
* Table 3  (2021)

However, the number of spaces might differ! So we will extract the table names automatically.

The ICD-10 codes used for causes of death:

>4) The ICD 10 codes for disease categories are as follows:	
Cancer: C00-C97	
Dementia and Alzheimer's: F01, F03 and G30	
Circulatory: I00:I99	
Respiratory: J00-J99	
COVID-19: U07

The format is a bit complicated to read automatically; we will extract the number of weeks available in the data from the filename.

~~These data come chopped up into 4 sheets, 2 by 2 for each of year 2020/2021 and all deaths/covid-related deaths. They are named:

* Table 1 (2020)
* Table 1 (2021)
* Table 2 (2020)
* Table 2 (2021)

~~

```{r}
weeks_available_in_nrs_weekly_data_by_cause_of_death_2021 <-  # extract the maximum weeks available from the weekly-updated 2021 data
  files_weekly_deaths$main_report %>%
  str_extract(string = ., pattern = "week-\\d{2}") %>%  # extract eg "week-12"
  str_extract(string = ., pattern = "\\d{2}") %>%  # extract "12"
  as.integer()

## extract the sheet names for cause of death data
nrs_weekly_data_sheet_2020 <- 
  excel_sheets(files_weekly_deaths$main_report)[which(str_detect(tolower(excel_sheets(files_weekly_deaths$main_report)), pattern = "table 3.*2020"))]
nrs_weekly_data_sheet_2021 <- 
  excel_sheets(files_weekly_deaths$main_report)[which(str_detect(tolower(excel_sheets(files_weekly_deaths$main_report)), pattern = "table 3.*2021"))]

## construct column names for the data
headers_in_nrs_data_2020 <-
  c(
    "place_of_death",
    "cause_of_death",
    paste0("week_", 1:53),
    "blank_remove",  # this and the rest are irrelevant entries that we'll remove
    "remove_1",
    "remove_2"
  )
headers_in_nrs_data_2021 <-
  c(
    "place_of_death",
    "cause_of_death",
    paste0(
      "week_",
      1:weeks_available_in_nrs_weekly_data_by_cause_of_death_2021
    ),
    "blank_remove",  # this and the rest are irrelevant entries that we'll remove
    "remove_1"
  )

## extract data... this is dense but I've tried to annotate it clearly!
weekly_deaths_cause_of_death_before_split_2020 <-
  readxl::read_excel(files_weekly_deaths$main_report, sheet = nrs_weekly_data_sheet_2020, col_names = headers_in_nrs_data_2020, range = cell_rows(6:125)) %>%  # the data are inrows 6:125
  select(-matches("remove")) %>%  # remove irrelevant summary columns at the end
  mutate(across(.cols = matches("week"), .fns = as.numeric)) %>%  # remove erroneous "count1, count2, ..." entries due to superscript in previous column
  mutate(dataset = if_else(condition = str_detect(string = cause_of_death, pattern = regex(pattern = "^registered|^difference", ignore_case = TRUE)), true = cause_of_death, false = NA_character_)) %>%  # extract the Registered deaths: historical, 2020/2021, and Difference sections
  tidyr::fill(place_of_death, .direction = "down") %>%  # complete the entries for place of death from the "last observed"
  tidyr::fill(dataset, .direction = "down") %>%  # same as above but for "dataset" column
  drop_na(week_1) %>%  # remove blank "header" rows with no data recorded
  pivot_longer(cols = matches("week"), names_to = "week_number", values_to = "number_of_deaths", values_drop_na = TRUE) %>%  # convert to long data format
  mutate(
    week_number = as.integer(parse_number(week_number)),  # extract week number
    place_of_death =  # find best match in the reference names used in other datasets
      order_of_place_of_death_levels[stringdist::amatch(x = str_sub(place_of_death,1,4), table = str_sub(order_of_place_of_death_levels,1,4), method = "lv", maxDist = 5)]  # the reference is in the variable order_of_place_of_death_levels
    )

weekly_deaths_cause_of_death_before_split_2021 <-
  readxl::read_excel(files_weekly_deaths$main_report, sheet = nrs_weekly_data_sheet_2021, col_names = headers_in_nrs_data_2021, range = cell_rows(6:125)) %>%  # the data are inrows 6:125
  select(-matches("remove")) %>%  # remove irrelevant summary columns at the end
  mutate(across(.cols = matches("week"), .fns = as.numeric)) %>%  # remove erroneous "count1, count2, ..." entries due to superscript in previous column
  mutate(dataset = if_else(condition = str_detect(string = cause_of_death, pattern = regex(pattern = "^registered|^difference", ignore_case = TRUE)), true = cause_of_death, false = NA_character_)) %>%  # extract the Registered deaths: historical, 2020/2021, and Difference sections
  tidyr::fill(place_of_death, .direction = "down") %>%  # complete the entries for place of death from the "last observed"
  tidyr::fill(dataset, .direction = "down") %>%  # same as above but for "dataset" column
  drop_na(week_1) %>%  # remove blank "header" rows with no data recorded
  pivot_longer(cols = matches("week"), names_to = "week_number", values_to = "number_of_deaths", values_drop_na = TRUE) %>%  # convert to long data format
  mutate(
    week_number = as.integer(parse_number(week_number)),  # extract week number
    place_of_death =  # find best match in the reference names used in other datasets
      order_of_place_of_death_levels[stringdist::amatch(x = str_sub(place_of_death,1,4), table = str_sub(order_of_place_of_death_levels,1,4), method = "lv", maxDist = 5)]  # the reference is in the variable order_of_place_of_death_levels
    )

## compile the weekly data
weekly_deaths_cause_of_death <-
  bind_rows(
    weekly_deaths_cause_of_death_before_split_2020 %>% filter(!str_detect(tolower(dataset), pattern = "difference|average")),
    weekly_deaths_cause_of_death_before_split_2021 %>% filter(!str_detect(tolower(dataset), pattern = "difference|average"))
  ) %>%
  mutate(
    year = as.integer(parse_number(dataset)),
    date_w_c = compute_start_date_from_week_number(week_number = week_number, year = year),
    week_number_run_over = if_else(year == 2021, 53L + week_number, week_number)  # invent a "run-over" week number - weeks 54+ are in 2021
    ) %>%
  select(-dataset)

## compile historical data - note that it's already summarised as average over the 5 year period, so we don't have the raw data, nor do we have minima/maxima
historical_average_cause_of_death <-
  weekly_deaths_cause_of_death_before_split_2020 %>%  # only data from the 2020 sheet are used - the 2021 data is the same entries for historical deaths!
  filter(str_detect(tolower(dataset), pattern = "average")) %>%
  select(-dataset) %>%
  rename(deaths_mean = number_of_deaths) %>%
  mutate(deaths_min = NA_real_, deaths_max = NA_real_)
```

### Load 'ad-hoc' query data

These are data aggregated by sex, age, and region (HB/LA)!

```{r}
# checking out structure

@@

# beds_raw <- 
#   read_csv("./beds_by_nhs_board_of_treatment_and_specialty.csv", guess_max = 3e4) %>%
#   mutate(ref_area = match_area(HB)) %>%  # clean health board names
#   clean_names() %>%
#   # select(-percentage_occupancy_qf) %>%
#   extract(col = quarter, into = c("year", "quarter"), regex = "(\\d{4})Q(\\d)", remove = TRUE) %>%
#   # mutate(across(.cols = matches("percent"), .fns = ~{.x / 100}))
#   mutate(percentage_occupancy = percentage_occupancy / 100)
# 
# beds_raw %>%
#   filter(ref_area == "Scotland") %>% count(specialty_name)
# 
# beds_raw %>%
#   filter(ref_area == "Scotland" & specialty_name == "Palliative Medicine") %>%
#   ggplot() +
#   aes(x = quarter, y = percentage_occupancy, colour = year, size = year) +
#   scale_y_continuous(labels = function(x) scales::percent(x), limits = c(0,NA)) +
#   # geom_point() +
#   geom_line(aes(group = year)) +
#   scale_colour_viridis_d() +
#   scale_size_manual(values = c(rep(0.5, times = 5),1)) +
#   NULL

@@

historical_weekly_average_overall <-
  past_deaths_overall %>%
  filter(year!="average") %>%  # remove averages
  group_by(year, week_number) %>%  # remove week 53 if it was 0 for all places  - this means there was no week 53!
  filter(!all(number_of_deaths==0 & week_number==53)) %>%
  ungroup %>%
  create_week_53_data_for_years_with_52_weeks %>%
  ungroup %>%
  group_by(week_number,place_of_death) %>% 
  summarise(
    across(number_of_deaths, .fns = list(mean=mean,min=min,max=max)),
    .groups = "drop"
  ) %>% rename_all(~str_replace_all(.x, pattern = "number_of_deaths", replacement = "deaths"))

@@

historical_weekly_average_hb <-
  past_deaths_hb %>%
  create_week_53_data_for_years_with_52_weeks() %>%
  group_by(
    week_number, place_of_death, ref_area
  ) %>%
  summarise(
    deaths_mean = mean(number_of_deaths),
    deaths_min = min(number_of_deaths),
    deaths_max = max(number_of_deaths),
    .groups = "drop"
  )

historical_weekly_average_la <-
  past_deaths_la %>%
  create_week_53_data_for_years_with_52_weeks() %>%
  group_by(
    week_number, place_of_death, ref_area
  ) %>%
  summarise(
    deaths_mean = mean(number_of_deaths),
    deaths_min = min(number_of_deaths),
    deaths_max = max(number_of_deaths),
    .groups = "drop"
  )

historical_weekly_average_sex_age <-
  past_deaths_sex_age %>%
  create_week_53_data_for_years_with_52_weeks() %>%
  group_by(
    week_number, place_of_death, age, sex
  ) %>%
  summarise(
    deaths_mean = mean(number_of_deaths),
    deaths_min = min(number_of_deaths),
    deaths_max = max(number_of_deaths),
    .groups = "drop"
  )

historical_weekly_average_age <-
  past_deaths_age %>%
  create_week_53_data_for_years_with_52_weeks() %>%
  group_by(
    week_number, place_of_death, age
  ) %>%
  summarise(
    deaths_mean = mean(number_of_deaths),
    deaths_min = min(number_of_deaths),
    deaths_max = max(number_of_deaths),
    .groups = "drop"
  )

historical_weekly_average_sex <-
  past_deaths_sex %>%
  create_week_53_data_for_years_with_52_weeks() %>%
  group_by(
    week_number, place_of_death, sex
  ) %>%
  summarise(
    deaths_mean = mean(number_of_deaths),
    deaths_min = min(number_of_deaths),
    deaths_max = max(number_of_deaths),
    .groups = "drop"
  )

@@

historical_annual_average_age <-
  past_deaths_age %>%
  compute_historical_annual_average_deaths(age)

historical_annual_average_cause_of_death <-  # this isn't quite the right figure because we don't have the raw data to work from, but weekly averages across 2015-2019
  historical_average_cause_of_death %>%
  group_by(place_of_death, cause_of_death) %>%
  summarise(
    annual_deaths_mean = sum(deaths_mean),
    annual_deaths_min = NA_real_,
    annual_deaths_max = NA_real_,
    .groups = "drop"
  )
```

@@

```{r}
weekly_deaths_overall %>%
  filter(sex=="all" & age=="all") %>%
  left_join(historical_weekly_average_overall) %>%
  select(year, week_number, place_of_death, deaths_nrs_past_average_all_causes, deaths_mean) %>%
  filter(round(deaths_nrs_past_average_all_causes) != round(deaths_mean)) %>%
  knitr::kable(caption = "Subset of weekly deaths where calculated mean deaths 2015-2019 differed between the COVID-19 related deaths file and the weekly deaths file (i.e. all other entries had the same figures!). Week 53 was computed as the average of deaths in week 53 in 2015 and week 52 in 2016-2019. For all the other datasets the mean deaths computed agree!")
```

@@

historical_weekly_average_hb <- compute_moving_average_for_historical_data(historical_weekly_average_hb)
historical_weekly_average_la <- compute_moving_average_for_historical_data(historical_weekly_average_la)
historical_weekly_average_sex_age <- compute_moving_average_for_historical_data(historical_weekly_average_sex_age)
historical_weekly_average_sex <- compute_moving_average_for_historical_data(historical_weekly_average_sex)
historical_weekly_average_age <- compute_moving_average_for_historical_data(historical_weekly_average_age)
```

@@

```{r}
## compute rolling average
merged_deaths_overall <-
  weekly_deaths_overall %>%
  filter(sex=="all" & age=="all") %>%
  inner_join(historical_weekly_average_overall %>% mutate(sex = "all", age = "all"),  # only merge for aggregated data b/c that's all we have!
            by = c("place_of_death", "week_number", "sex", "age"))

merged_deaths_hb <-
  rolling_deaths_hb %>%  # use data with rolling movingincluded
  inner_join(historical_weekly_average_hb, by = c("week_number","ref_area","place_of_death"))

merged_deaths_la <-
  rolling_deaths_la %>%  # use data with rolling movingincluded
  inner_join(historical_weekly_average_la, by = c("week_number","ref_area","place_of_death"))

merged_deaths_sex_age <-
  rolling_deaths_sex_age %>%  # use data with rolling movingincluded
  inner_join(historical_weekly_average_sex_age, by = c("place_of_death", "week_number", "sex", "age"))

merged_deaths_sex <-
  rolling_deaths_sex %>%
  inner_join(historical_weekly_average_sex, by = c("place_of_death", "week_number", "sex"))

merged_deaths_age <-
  rolling_deaths_age %>%
  inner_join(historical_weekly_average_age, by = c("place_of_death", "week_number", "age"))

merged_deaths_cause_of_death <-
  weekly_deaths_cause_of_death %>%
  inner_join(
    historical_average_cause_of_death  , by = c("place_of_death", "week_number", "cause_of_death")
  )
```

@@

total_deaths_overall <-
  merged_deaths_overall %>%
  compute_total_deaths_in_year() %>%
  left_join(historical_annual_average_overall, by = c("place_of_death")) %>%
  compute_ratio_of_annual_deaths_to_historical

## bespoke computation because format is different... deaths split by cause!
total_deaths_cause_of_death <-
  merged_deaths_cause_of_death %>%
  group_by(year, place_of_death, cause_of_death) %>%
  summarise(deaths = sum(number_of_deaths), .groups="drop") %>%
  left_join(historical_annual_average_cause_of_death, by = c("place_of_death", "cause_of_death")) %>%
  mutate(
    ratio_annual_deaths_to_historical_mean = deaths / annual_deaths_mean
  )
```

@@

date_range_text <- glue::glue("Data from w/c {format(earliest_date, '%d %B %Y')} to w/c {format(most_recent_date_available_2021, '%d %B %Y')} (inclusive).")

@@

# Deaths by cause of death

## Annual deaths by cause

```{r}
(figure_annual_deaths_by_cause <-
  total_deaths_cause_of_death %>%
  filter(year == 2020 & cause_of_death!="All" & !place_of_death %in% c("Other","All")) %>%
  # pivot_longer(cols = c(deaths, annual_deaths_mean), names_to = "deaths_type", values_to = "deaths") %>%
  ggplot() +
  # geom_col(aes(x = cause_of_death, fill = cause_of_death, y = deaths, group = deaths_type, linetype = deaths_type), position = "dodge", colour = "grey10") +
  geom_col(aes(x = cause_of_death, fill = cause_of_death, y = deaths), position = "dodge", colour = "grey10") +
  geom_point(aes(x = cause_of_death, y = annual_deaths_mean), position = "dodge", colour = "grey10") +
  scale_fill_viridis_d() +
  facet_wrap(~place_of_death) +
  NULL
)
```

## By cause, at home

```{r, fig.width=12, fig.height=9, warning=FALSE}
(figure_deaths_at_home_by_cause <-
  merged_deaths_cause_of_death %>%
  filter(str_starts(place_of_death,"Home")) %>%
  filter(cause_of_death != "All") %>%
  # filter(!place_of_death %in% c("All","Other")) %>%
  pivot_longer(cols = c(deaths_mean, number_of_deaths), names_to = "deaths_type", values_to = "number_of_deaths") %>%
  filter(!(deaths_type=="deaths_mean"&cause_of_death=="COVID-19")) %>%  # remove historical average for covid, it's 0 anyway
  mutate(place_of_death = factor(place_of_death, levels = c("Hospital", "Home & other non-institution", "Care home"))) %>%  # needs to be factor with same levels, otherwise it messes up level order when added as geom_text later!)
  ggplot(aes(x = date_w_c)) +
  # annotate(geom = "rect", xmin = compute_start_date_from_week_number(week_number = 1, year_number = 2021), xmax = compute_start_date_from_week_number(week_number = weeks_available_2021, year_number = 2021), ymin = -Inf, ymax = Inf, fill = "grey90", alpha = 0.2) +  # shade area - geom_rect doesn't work here
  scale_x_date(date_labels = "%d-%m-%y", date_breaks = "8 weeks", limits = c(earliest_date, most_recent_date_available_2021)) +
  geom_line(aes(y = number_of_deaths, colour = cause_of_death, linetype = deaths_type)) +
  scale_colour_viridis_d() +
  scale_linetype_manual(labels = c("Historic mean 2015-2019","Deaths since 2020"), values = c("dashed","solid")) +
  # geom_line(aes(y = number_of_deaths  , colour = deaths_type)) +
  # geom_line(aes(y = deaths_mean), linetype = "dashed", colour="grey20") +
  facet_wrap(cause_of_death~place_of_death, scales = "free_y") +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    plot.caption = element_text(size = 10, colour = "gray60"),
    plot.margin = margin(5, 15, 5, 5),
    axis.text.x = element_text(angle = 60, colour = "gray40", vjust=1, hjust=1)
  ) +
  labs(x = "Date w/c",
       y = "Weekly Deaths (N)",
       subtitle = date_range_text,
       caption = paste0(c("Note that y-axis scale varies across panels!",death_registrations_text,removed_other_category_text,source_nrs_text), collapse="\n")
       ) +
  NULL
)

save_output_file(filename = paste0(dir_outputs,"/figure_deaths_at_home_by_cause"), extensions = c(".pdf",".svg",".png"), plot = figure_deaths_at_home_by_cause, width = 28, height = 14, dpi = 300, units = "cm")
```
